---
title: "Wives"
output: html_document
menu:
  after:
    name:
    weight: 2
---
 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse) 
library(readxl)
library(plotly)
library(scales)
library(RColorBrewer)
library(kableExtra)
contracts <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/contracts_gender_r_2.xlsx")
defs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/defs_r.xlsx")
plfs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/plfs_r.xlsx")
parties <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/parties_r.xlsx")
cites <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/cites_for_contracts.xlsx")
gendertotaltable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/gendertotaltable.xlsx")
partnertable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/partner_table.xlsx")
couples <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/couples.xlsx")

names(gendertotaltable)[1] <- "gender"
names(gendertotaltable)[5] <- "percentage"
opts <- options(knitr.kable.NA = "")

parties <- parties %>%
  full_join(cites)
names(parties)[4] <- "name"
contracts <- contracts %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

names(parties)[9] <- "cite"

n_parties_joiner <- parties %>%
  group_by(cite) %>%
  count() %>%
  mutate(n_parties = n) %>%
  select(cite, n_parties)

parties <- parties %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

contracts <- contracts %>%
  full_join(n_parties_joiner)

```



## Marriage and Family 

57% of the women in the casebook appear with (or regarding) a spouse or partner, as opposed to 19% of men. 13% of women are described regarding some other familiar relationship (aunt, sister, mother, etc.) as opposed to 10% of men. In all, nearly 3 of every 4 women are described by their familiar relations as opposed to less than a third of men. 

```{r, echo = FALSE, warning = FALSE, message = FALSE}
names(partnertable) <- c("","partner","%partner","family","%family","partner+family","%p+f")

```

```{r, echo = FALSE, warning = FALSE, message = FALSE}



parties_business <- parties %>%
  filter(transaction == "Business", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/31) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("hotpink3","chartreuse4")) +
  labs(title = "Business-Business Transaction Gender Breakdown") 

a <- parties %>%
  filter(typenomf == "Man" | typenomf == "Woman" | typenomf == "Unknown" ) %>%
  group_by(typenomf) %>%
  mutate(typea = n()) %>%
  ungroup() %>%
  group_by(typenomf,spouse) %>%
  mutate(typeb = n()) %>%
  mutate(percentage = paste(sep = "", str_sub(as.character(typeb/typea),3,4),"%")) %>%
  ggplot(aes(typenomf, fill = spouse)) + 
  geom_bar(aes(text = paste(sep = "", typeb,", ",percentage))) +
  scale_fill_discrete(name = "Family/Spousal\nStatus", breaks = c("Y","F","N"), labels = c("Spouse/Partner","Family Member","Unrelated"))
ggplotly(a, tooltip = "text")  

```

### The (Un)Happy Couples 

Most of these are members of one of the 24 couples who appeared with or against a heterosexual partner in a relationship. 


```{r, echo = FALSE, warning = FALSE, message = FALSE}
partnertable %>%
  knitr::kable() 
couples1 <- couples %>%
  filter(couple == 1)
couples2 <- couples %>%
  filter(couple ==2)
couples3 <- couples %>%
  filter(couple == 3)
couples4 <- couples %>%
  filter(couple ==4)

couples_table <- couples1 %>%
  right_join(couples2,by=c("page","year","transaction","cite","simplecite")) %>%
  select(name.x,name.y,page,simplecite)

couples_table2 <- couples3 %>% 
  right_join(couples4,by=c("page","year","transaction","cite","simplecite")) %>%
  select(name.x,name.y,page,simplecite)

couples_table <- full_join(couples_table, couples_table2)

kable(couples_table, "html", caption = "Couples in KCP") %>%
  kable_styling(fixed_thead = TRUE) %>%
  scroll_box(height = "300px") 


```



## Relevant Non-Party Spouses

Two men and two women had their relationships described with reference to the proceedings but without their partner appearing. 

### Katz v. Danny Dare Inc.
#### 610 S.W.2d 121 (Mo. Ct. App. 1980)
#### KCP 248

I.G. Katz brought a promissory estoppel claim against a company the president of which “was also the brother of Katz’s wife,” establishing the connection between Katz and the company; moreover, his wife would benefit from a Social Security clause in the promised contract.

### Credit Bureau Enter. v. Pelo
#### 608 N.W.2d 20 (Iowa 2000)
#### KCP 297

Russell N. Pelo was involuntarily committed to a hospital after he telephoned his wife to make threats of self harm, relevant to the context of his refusal to pay. 

### Locke v. Warner Bros., Inc. 
#### 57 Cal. App. 4th 354 (1997)
#### KCP 513

Sondra Locke’s dispute with Warner Bros. is framed as something patronizingly set up for her by her ex Clint Eastwood (not a party), relevant to the argument about good faith.

### King v. Trustees of Boston Univ.
#### 420 Mass. 52 (1995)
#### KCP 237

Coretta Scott King brings her case on behalf of her family estate, and is actually a great example of rhetoric relating a woman to a husband but still giving her full agency: 

> *“The plaintiff, Coretta Scott King, in her capacity as administratix of the estate of her late husband, and in her individual capacity, appeals...”*

## Barely Relevant Non-Party Status. 

One man and one woman had their marital status described as a strange, but seemingly purposeful, aside. 

### Dohrmann v. Swaney
#### 14 N.E.3d 605 (Ill. 2014)
#### KCP 129

Dohrmann v. Swaney: “Dohrmann was a 40-year-old neurosurgeon, married to Dr. Helen Dohrmann” 130, where his and his wifes’ professional status establish a class level in this case about fraud? 

### Aceves v. U.S. Bank N.A.
#### 120 Cal. Rptr. 3d 507 (Cal. Ct. App. 2011)
#### KCP 255

In Aceves v. U.S. Bank, N.A. the judge present the plaintiff, a woman independently bringing a suit whose spouse appears only as a minor detail in the rest of the opinion, as “Claudia Aceves, a married woman.” (255) The case is about bankruptcy – perhaps her marriage establishes some kind of moral credibility? 

